---
title: "ROMS grid"
author: "mdsumner"
date: "February 25, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## ROMS grid

Regional Ocean MOdelling System (ROMS) uses a horizontal curvilinear coordinates, which needs special care for use in Cartesian or other coordinate systems. 

The material discussed here is sourced this:  [discussion on 'Curvlinear Coordinates'](https://www.myroms.org/forum/viewtopic.php?f=3&t=295) on the [Ocean Modeling Discussion](https://www.myroms.org) forum. 


This file contains a subset of a ROMs model. 

```{r}
library(raadtools)
romsfile <- file.path(getOption("default.datadir"), 
                      "data_local", "acecrc.org.au", 
                      "ROMS", "s_corney", 
                      "cpolar", "ocean_his_3101_uvwtempsalt.nc")

## print out the ncdump header
#print(raster(romsfile))
```

A tidier (than `ncdump -h`) summary can be obtained with the `rancid` package. 

The most important variables for this discussion are `lon_u`, `lat_u`, `angle`. 

```{r}
library(rancid)
roms <- NetCDF(romsfile)
library(dplyr)
## what vars?
vars(roms) %>% select(name, ndims, units, longname)
```

Obtain the `lon_u`, `lat_u` and `angle` variables as `RasterLayer` objects. 

```{r}
library(angstroms)
lon_u <- romsdata(romsfile, "lon_u")
lat_u <- romsdata(romsfile, "lat_u")

angle <- romsdata(romsfile, "angle")
u <- romsdata(romsfile, "u", slice = c(1, 1))
v <- romsdata(romsfile, "v", slice = c(1, 1))

mesh <- as.matrix(crop(brick(lon_u, lat_u, u, v, angle), extent(400, 600, 30, 180)))
plot(mesh, pch = ".")
