---
title: "ROMS mapping"
author: "Michael Sumner"
date: "15/01/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Basic R tools to deal with ROMS and make maps. 

First, load up some packages and find out the variables in the file, extract one out, get the X-Y coordinates for this data and find the boundary in the real world for the model. 


```{r}
roms_path <- file.path(getOption("default.datadir"), "data_local/acecrc.org.au/ROMS/mertz_sample/mer_his_1992_01.nc")
library(angstroms)    ## devtools::install_github("mdsumner/angstroms")
library(ncdump)       ## devtools::install_github("r-gris/ncdump")
library(tabularaster) ## devtools::install_github("r-gris/tabularaster")
library(rworldmap)
ncd <- NetCDF(roms_path)

ncd$variable$name

```

Let's choose `u`, and read the first available XY-slice, also read the grid's coordinates and derive the boundary. 

```{r}

vname <- "u"
dd <- romsdata(roms_path, varname = vname, slice = c(1, 1), transpose = TRUE)
plot(dd)  ## this is pure 0-dimX, 0-dimY index space
longlat <- romscoords(roms_path, transpose = TRUE)
contour(longlat[[1]], add = TRUE, lty = 2)
contour(longlat[[2]], add = TRUE, lty = 2)
bound <- boundary(longlat)
projection(bound) <- "+init=epsg:4326"
extent(bound)
```


Now, plot this region in the "real world", but first choose a local map projection. 

```{r}
pbound <- spTransform(bound, "+proj=lcc +lat_0=-65 +lat_1=-72 +lat_2=-60 +lon_0=147 +ellps=WGS84 +no_defs")
plot(pbound)
data(countriesLow)
w <- spTransform(countriesLow, projection(pbound))
plot(w, add = TRUE)
library(rgdal)
op <- par(xpd = NA)
llgridlines(pbound)
par(op)
# lon_grat <- rasterToContour(longlat[[1]]); projection(lon_grat) <- "+init=epsg:4326"
# lat_grat <- rasterToContour(longlat[[2]]); projection(lat_grat) <- "+init=epsg:4326"
# plot(spTransform(lon_grat, projection(pbound)), add = TRUE, lty = 2)
# plot(spTransform(lat_grat, projection(pbound)), add = TRUE, lty = 2)
```


```{r}
library(leaflet)
set_crs <- function(x, value) {
  projection(x) <- value
  x
}
epsg3857 <- "+init=epsg:3857 +proj=merc +a=6378137 +b=6378137 +lat_ts=0.0 +lon_0=0.0 +x_0=0.0 +y_0=0 +k=1.0 +units=m +nadgrids=@null
+no_defs"
dd1 <- dd
set_ext <- function(x) setExtent(x, extent(c(xmin(x), xmax(x), ymin(x), ymax(x)) * 10))

get_slice <- function(i = 1) {
  r <- romsdata(roms_path, varname = vname, slice = c(i, 1), transpose = TRUE)
  set_ext(set_crs(dd, epsg3857))
}
leaflet() %>% addRasterImage(get_slice())

```


```{r}
## what dims does our var have?
dm <- ncd$variable %>% filter(name == "u") %>% select(id) %>% inner_join(ncd$vardim) %>% inner_join(ncd$dimension, c("dimids" = "id"))
dm

## choose s_rho 
zd <- "s_rho"
zn <- (dm %>% filter(name == zd))$len


```
